```{r, message = FALSE, warning = FALSE}
set.seed(1) # To be able to replicate the k-means

library(tidyverse)
library(cluster)
library(Rtsne)
library(seriation)
library(stargazer)

```

## Including Plots

You can also embed plots, for example:

What if we used two beta-binomial posterior distributions each for two different "types" of districts (we will determine those by who has higher turnout), to determine turnout for democrats in different cities in fairfax county?

```{r}
#to_cluster <- read.csv(file.choose())

#to_cluster <- read.csv('2016_Election_Results__Voter_Turnout.csv')

dem <- read.csv('dem.csv')
rep <- read.csv('rep.csv')
set.seed(1235)


plot(dem$誰..OBJECTID, dem$PERCVOTE)
plot(rep$誰..OBJECTID, rep$PERCVOTE)

names(dem)[names(dem) == "誰..OBJECTID"] <- "OBJECTID"
names(rep)[names(rep) == "誰..OBJECTID"] <- "OBJECTID"

myvars <- c("OBJECTID", "REGVOTERS", "TOTBALLOTSLINK", "PERCVOTE")
dem_edt <- dem[myvars]
rep_edt <- rep[myvars]

numb <- length(dem_edt[,1])
#df <- to_cluster %>%
#  na.omit() %>%
#  sample_n(243)
```

```{r}

betabinom_post <- function(N, a, b, numsamp){
  prior <- rbeta(numsamp, a, b)
  likelihood <- rbinom(numsamp, N, prior)
  post <- rbeta(numsamp, a+likelihood, b+N-likelihood)
  return(post)
}
N <- 1000
ab_m <- matrix(c(0.7, 0.3, 0.3, 0.7),
               nrow = 2,
               ncol = 2,
               byrow=TRUE) #the first row is a democrat city's voting alpha and beta

dem_voter <- rep(0, numb)
dem_perc <- rep(0, numb)
err <- rep(0, numb)
city_id <- rep(0, numb)

for (i in 1:numb){
  vote_id <- 1 #first row (democrat)
  if (rep_edt$TOTBALLOTSLINK[i] > dem_edt$TOTBALLOTSLINK[i]){
    vote_id <- 2
  }
  city_id[i] <- vote_id
  post <- betabinom_post(rep_edt$REGVOTERS[i], ab_m[vote_id ,1], ab_m[vote_id, 2], 1000)
  dem_perc[i] <- mean(post)
  dem_voter[i] <- rep_edt$REGVOTERS[i] * dem_perc[i]
  err[i] <- (dem_voter[i]-dem_edt$TOTBALLOTSLINK[i])/dem_edt$TOTBALLOTSLINK[i]
}

plot(err)
mean(err)

```


```{r}

get_dem_turnout_error <- function(a_dem, b_dem, a_rep, b_rep){
  ab_m <- matrix(c(a_dem, b_dem, a_rep, b_rep),
               nrow = 2,
               ncol = 2,
               byrow=TRUE) #the first row is a democrat city's voting alpha and beta

  dem_voter <- rep(0, numb)
  #dem_perc <- rep(0, numb)
  err <- rep(0, numb)
  city_id <- rep(0, numb)

  for (i in 1:numb){
    vote_id <- 1 #first row (democrat)
    if (rep_edt$TOTBALLOTSLINK[i] > dem_edt$TOTBALLOTSLINK[i]){
      vote_id <- 2
    }
    city_id[i] <- vote_id
    post <- betabinom_post(rep_edt$REGVOTERS[i], ab_m[vote_id ,1], ab_m[vote_id, 2], 1000)
    dem_perc <- mean(post)
    dem_voter[i] <- rep_edt$REGVOTERS[i] * dem_perc
    err[i] <- abs(dem_voter[i]-dem_edt$TOTBALLOTSLINK[i])/dem_edt$TOTBALLOTSLINK[i]
  }
  return(cbind(city_id, dem_voter, err))
}

get_dem_turnout_i <- function(i, a_dem, b_dem, a_rep, b_rep){
  ab_m <- matrix(c(a_dem, b_dem, a_rep, b_rep),
               nrow = 2,
               ncol = 2,
               byrow=TRUE) #the first row is a democrat city's voting alpha and beta


    vote_id <- 1 #first row (democrat)
    if (rep_edt$TOTBALLOTSLINK[i] > dem_edt$TOTBALLOTSLINK[i]){
      vote_id <- 2
    }
    city_id <- vote_id
    post <- betabinom_post(rep_edt$REGVOTERS[i], ab_m[vote_id ,1], ab_m[vote_id, 2], 1000)
    dem_perc <- mean(post)
    dem_voter <- rep_edt$REGVOTERS[i] * dem_perc
    #err[i] <- (dem_voter[i]-dem_edt$TOTBALLOTSLINK[i])/dem_edt$TOTBALLOTSLINK[i]
  return(dem_voter)
}
```

```{r}

a_dem <- 0.1
b_dem <- 0.5
a_rep <- 0.3
b_rep <- 2

res <- get_dem_turnout_error(a_dem, b_dem, a_rep, b_rep)

plot(res[,1], res[,3])

# It seems like both "republican" and "democrat" types of cities prefer a beta that is higher than its alpha in the prior beta distribution. What this means is that both "types" of cities, as defined by our model, skew towards voting republican
# We determined what "type" a city has by whether they had higher republican or democrat turnout. This is apparently due to the lack of detail in our model with the beta distribution assumed as our prior and a likelihood determined by a binomial
# It is clear that we need better models
```

```{r}
#idx <- seq(1, numb, 1)
#df <- data.frame(x = idx, y = dem_edt$TOTBALLOTSLINK)

#a_dem <- 0.7
#b_dem <- 0.3
#a_rep <- 0.3
#b_rep <- 0.7

#result <- nlsLM(y ~ get_dem_turnout_i(x, a_d, b_d, a_r, b_r),
#              data = df,
#              start = list(a_d = a_dem, b_d = b_dem, a_r = a_rep, b_r = b_rep),
#              control = nls.lm.control(ftol=2000))

#control = nls.lm.control(minFactor = 1/50000, tol=0.02)
```

```{r}
summary(result)
```

```{r}
drop_extreme <- function(x){
  
  x <- as.numeric(x)
  pct_95 <- quantile(x, probs = 0.95, na.rm = TRUE)[[1]]
  pct_5 <- quantile(x, probs = 0.05, na.rm = TRUE)[[1]]
  
  case_when(
    x < pct_5 ~ pct_5,
    x > pct_95 ~ pct_95,
    TRUE ~ x
  )
}

gower_standard_cont <- function(x){
  max <- max(x, na.rm = TRUE)
  min <- min(x, na.rm = TRUE)
  
  x/(max - min)
} 

quantile(to_cluster$PERCVOTE, probs = 0.95)[[1]]

to_cluster <- df %>% 
  .[, -1] %>% #filter( != "OBJECTID") %>%
  mutate_at(c("NAME", "COUNTY", "PRECINCTID", "NAME_1", "REGVOTERS","TOTBALLOTS","PERCVOTE", "INPERSON", "Shape__Area", "Shape__Length"), 
            drop_extreme) %>%
  mutate_at(c("COUNTY", "REGVOTERS", "TOTBALLOTS", "Shape__Area", "Shape__Length"), 
            gower_standard_cont) 

#to_cluster %>%
  #select(OBJECTID, NAME) %>/%
  #skimr::skim()
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r, error = FALSE, warning = FALSE, message = FALSE, results = 'asis'}
#library(poisson)

the_poisson <- glm(INPERSON ~ REGVOTERS + 
                 #log(PERCVOTE) + 
                 log(Shape__Area), #+ 
                 #log(Shape__Length), 
               data = to_cluster,
               family = poisson(link = 'log'))

stargazer(the_poisson, title = 'Main Poisson Model')

fit <- predict(the_poisson)
res <- resid(the_poisson)

myols <- lm(INPERSON ~ REGVOTERS + 
                 #log(PERCVOTE) + 
                 log(Shape__Area), #+ 
                 #log(Shape__Length), 
               data = to_cluster)

stargazer(myols, title = 'Main OLS Model')


```

```{r}
ggplot(to_cluster) + 
  aes(y = INPERSON, x = log(Shape__Area)) + 
  geom_point(col = 'cyan4') + 
  theme_light()

ggplot(to_cluster) + 
  aes(y = REGVOTERS, x = INPERSON) +
  geom_point(col = 'cyan4') + 
  theme_light()
```

```{r}
# install.packages('cluster')
library(cluster)

my_kmeans <- kmeans(to_cluster[, c('REGVOTERS', 'INPERSON', 'Shape__Length')], 4)

# As Registered Voters increase, so does INPERSON and Shape__Length.
## Cluster 2 has the highest means; Cluster 4 has the lowest.
my_kmeans 

clusplot(to_cluster[, c('REGVOTERS', 'INPERSON', 'Shape__Length')],
         my_kmeans$cluster,
         main = 'Clusters by REGVOTERS, INPERSON, and Shape__Length')
```

```{r}
#daisy(to_cluster[, c('REGVOTERS', 'INPERSON', 'Shape__Length')])
```

```{r, results = 'asis', warning = FALSE}
# Modeling by cluster

# Identify which rows belong to which cluster
to_cluster$cluster <- my_kmeans$cluster

# Estimate Poisson models
models_subsets_poisson <- to_cluster %>%
  split(.$cluster) %>%
  map(~ glm(INPERSON ~ REGVOTERS + log(Shape__Area), .x, family = poisson(link = 'log')))

# Precinct size matters for a couple clusters in Poisson model
with(models_subsets_poisson, 
     stargazer(`1`, `2`, `3`, `4`, 
               title = 'Poisson Subset Models by Cluster'))

# Estimate OLS models
models_subsets_ols <- to_cluster %>%
  split(.$cluster) %>%
  map(~ lm(INPERSON ~ REGVOTERS + log(Shape__Area), .x))

# Precinct size does not matter for OLS
with(models_subsets_ols, 
     stargazer(`1`, `2`, `3`, `4`, 
               title = 'OLS Subset Models by Cluster'))
```

# Residual Diagnostics

## Poisson
```{r}
hist(resid(the_poisson))

poisson_clusters <- paste('Poisson Cluster', 1:4)

par(mfrow = c(2,2))
for (i in seq_along(models_subsets_poisson)) {
  
  hist(resid(models_subsets_poisson[[i]]), main = poisson_clusters[i],
       xlab = 'Residuals')
  
}
```

## OLS
```{r}
hist(resid(myols))

ols_clusters <- paste('OLS Cluster', 1:4)

par(mfrow = c(2,2))
for (i in seq_along(models_subsets_ols)) {
  
  hist(resid(models_subsets_ols[[i]]), main = ols_clusters[i],
       xlab = 'Residuals')
  
}
```

## Comparing Median Residuals
```{r}
median(resid(the_poisson))
median(resid(myols))

# Median residuals for each poisson cluster model
map_df(models_subsets_poisson, ~ median(resid(.x)))

# Median residuals for each OLS cluster model
map_df(models_subsets_ols, ~ median(resid(.x)))

```
